\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Christopher M Finazzo Resume},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

\title{Christopher M Finazzo Resume}
\date{}

\begin{document}
\maketitle

\textbf{Christopher M. Finazzo}

\url{http://www.linkedin.com/in/chrisfinazzo}

{973.906.0496}{\href{mailto:chris@chrisfinazzo.com}{\nolinkurl{chris@chrisfinazzo.com}}}\\

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

\textbf{COMMUNICATIONS PROFESSIONAL}

Results driven individual with a passion for conveying complex ideas to
technical and nontechnical audiences in a way that is accurate, clear,
and concise. Proven ability to create audience appropriate messages with
a range of authoring tools. Strong verbal and written communication
skills as well as the ability to multitask, set priorities, and meet
deadlines.

\textbf{DEMONSTRATED EXPERTISE}

\begin{itemize}
\tightlist
\item
  Corporate Communications
\item
  Public Relations
\item
  Employee Communications
\item
  Media Relations
\end{itemize}

\begin{itemize}
\tightlist
\item
  Social Media
\item
  Email Production
\item
  Content Management Systems
\item
  HTML, CSS, and SASS
\end{itemize}

\begin{itemize}
\tightlist
\item
  AP \& APA Style
\item
  Adobe Creative Suite
\item
  Microsoft Office
\item
  Final Cut Pro
\end{itemize}

~

\textbf{PROFESSIONAL EXPERIENCE}

{\textbf{ALLIANT TECHNOLOGIES,} Morristown, NJ}{ Nov 2010 - Mar 2011}\\
\textbf{AMS Drawbridge Intern}

\begin{itemize}
\tightlist
\item
  Provided end-user support for customers using RSA tokens (Drawbridge
  2-factor authentication service).
\item
  Provisioned and managed token inventory for clients, including new
  orders, reassignments, and suspensions. Maintained current token stock
  for future orders.
\item
  Worked with customers to resolve authentication issues, escalating
  support tickets to Senior Engineers/Internal IT Support as necessary.
\item
  Worked with customer contacts (Internal IT) to resolve support
  requests
\item
  Revised documentation and support procedures as necessary to improve
  the process, created procedural workflows (Visio) to show changes over
  time.
\item
  Assisted Tier 1 engineers as necessary to resolve circuit and routing
  issues for customers, escalating issues to Service Providers when
  appropriate.
\end{itemize}

{\textbf{BOROUGH OF CHATHAM,} Chatham, NJ}{ Jul 2009 - Sep 2009}\\
\textbf{Intern}

\begin{itemize}
\tightlist
\item
  Created a survey to assess potential renovation options for Memorial
  Pool and gauge community support for the project.
\item
  Worked closely with 3rd-party vendors to develop a new email
  specification for more efficient communication with residents.
\item
  Gathered and compiled updated information for the Borough's Open Space
  \& Recreation Plan.
\item
  Collaborated with other departments to create an updated Policies \&
  Practices manual.
\item
  Updated internal documentation systems, digitized records as needed.
\end{itemize}

{\textbf{MASS TRANSMIT,} New York, NY}{ Jun 2008 - Aug 2008}\\
\textbf{Design \& Production Intern}

\begin{itemize}
\tightlist
\item
  Took HTML email production through static comps, programming,
  validation, testing, and distribution using Email Transmit (Web
  application for email marketing campaigns).
\item
  Integrated WordPress into a redesigned site launch for EGM Green,
  learned basics of server-side programming.
\item
  Developed an early prototype of SEGA Entertainment USA's World Sports
  Grille site using HTML, CSS, and PHP.
\item
  Updated database information for content systems through a custom CMS
  interface as part of a 4RealFoods site launch.
\item
  Created an in-house wiki (Media Wiki) to manage the internal
  technology infrastructure and store client information.
\item
  Learned basics of System Administration (Mac OS X, Linux)
\end{itemize}

{\textbf{RIDER UNIVERSITY,} Lawrenceville, NJ}{ Jan 2008 - Jun 2008}\\
\textbf{CIS Technology Lab Monitor}

\begin{itemize}
\tightlist
\item
  Monitored students working in the CIS Technology Lab.
\item
  Troubleshot computer problems
\item
  Assisted students with hardware and software.
\end{itemize}

{\textbf{LEHMAN BROTHERS,} New York, NY}{ May 2007 - Aug 2007}\\
\textbf{IT Summer Analyst}

\begin{itemize}
\tightlist
\item
  Coordinated a series of training sessions (Lunch `n' Learn) related to
  firmwide technology initiatives. Managed event scheduling,
  setup/teardown, and provided logistical support during the sessions.
  Created a calendar to manage these events.
\item
  Assisted with production duties related to a Global Technology
  Services town hall meeting. Managed attendance records, event
  setup/teardown, and provided logistical support as needed during the
  meeting.
\item
  Researched employee gift options for a Global Technology Services
  offsite meeting. Collaborated with 3rd-party vendors to evaluate
  sample products and estimate costs. Presented results to management
  for evaluation.
\item
  Drafted a monthly newsletter for the Global Technology Services'
  intranet (IT Portal). Compiled IT Portal feedback reports related to
  content and functionality. Created an archive of past newsletters.
\item
  Worked with technology groups to develop and distribute targeted
  communications related to the availability of systems and testing
  environments.
\end{itemize}

\textbf{EDUCATION}

Fairleigh Dickinson University, Madison, NJ -- Master of Arts, Class of
2013, Corporate \& Organizational Communication

Rider University, Lawrenceville, NJ -- Bachelor of Arts, Class of 2009,
Major -- Communications (Web Design), Double Minor -- Advertising and
Computer Information Systems

\end{document}
